### 2020-06-24 Documents/ESA/sections/LitReview.tex
minor mods in intro

\begin{itemize}
    \item Stability, that a system will return to the desired setpoint (or within a neighbourhood) if
    perturbed.

    \item Robustness, that a system will perform its function in the presence of uncertainty and
    noise

    \item Optimality, that the system will achieve some defined function

    \item Feasibility, that the controller will always be able to generate a control law which
    satisfies the desired properties.
\end{itemize}

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control communnity is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}

Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once.

@@

Of all of these systems, cooperative control has found greatest applicability in autonomous systems
\cite{Negenborn2014}, perhaps due to the favourable stability properties \cite{Venkat2006}. One
particularly strong application of this system is in vehicle platooning. Here, self-driving cars or
unmanned aerial vehicles (UAVs) must move in a certain formation without colliding into one another.
A number of examples can be found such as in \cite{Liu2019, VanParys2017, Zheng2017}. Distributed
MPC provides the advantage that guarantees can be placed regarding coupled constraint satisfaction
and feasibility.

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that Inoue
et al have identified this problem and are currently working towards its incorporation into the
model.

It would, therefore, be of particular interest from a safety perspective to consider agent
interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
swarm system to include agent interaction. This presents a first step towards considering the swarm
as composed of intelligent agents rather than mindless particles and, as the authors suggest,
presents the possibility of applying game theoretic approaches towards swarms, which also gives the
ability to consider heterogeneous swarm systems who interact with one another through repeated play.
Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
leader-follower swarm system to achieve given tasks.

@@

The reduction of the complexity in interactions between agents also allows for the robots to perform
other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).

@@

@@

It is clear that each method presents its own set of advantages and disadvantages. In fact, the
greater contributions are made from a unification of techniques (e.g. game theoretic control) which
leverage the strengths of one technique to mitigate the drawbacks of another. To this end, we
consider the unification of swarm control and multi-agent learning. The aim is to unify the
strengths of swarm theory, MPC and game theory to study populations of agents who can make
decisions on an individual basis but perform tasks through large scale collaboration. In the
subsequent chapters, we propose a line of research which explores the properties of a system as well
as establishing practical control methodologies along the way.

>>>>

\begin{itemize}
    \item {\em Stability}: a system will return to the desired setpoint (or within a neighbourhood) if
    perturbed.

    \item {\em Robustness}: a system will perform its function in the presence of uncertainty and
    noise

    \item {\em Optimality}: the system will achieve some defined function

    \item {\em Feasibility}: the controller will always be able to generate a control law which
    satisfies the desired properties.
\end{itemize}

There are a number of approaches towards control systems. However, the
interest of this review lies in multi-agent systems which must operate
in the face of uncertainty. As such, we focus on stochastic and
distributed control. The relevant literature of the control community
is vast and can be divided into a number of sub-fields. We consider
Distributed MPC (DMPC) and Swarm Optimal Control as those which are
particularly relevant to this study and review them hereafter.

\subsection{Distributed Model Predictive Control} \label{sec::Distributed_MPC}

Rawlings et al.~\cite{rawlings2017model} divide the problem of
distributed control into four distinct categories: decentralised
control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only
considers the case in which a centralised controller has access and
can manipulate multiple agents at once \fr{so then?}.

@@

Of all of these systems, cooperative control has found greatest
applicability in autonomous systems \cite{Negenborn2014}, perhaps due
to the favourable stability properties \cite{Venkat2006}. One
particularly strong application of this approach is in vehicle
platooning. Here, self-driving cars or unmanned aerial vehicles (UAVs)
must move in a certain formation without colliding into one another.
A number of examples can be found such as in \cite{Liu2019,
  VanParys2017, Zheng2017}. Distributed MPC provides the advantage
that guarantees can be placed regarding coupled constraint
satisfaction and feasibility.

@@

The above models come under the term `mean-field models’
\cite{Elamvazhuthi2019b}, a series of equations for stochastic forward
processes (such as swarm foraging) in which, as the number of agents
tends to infinity, the true macroscopic motion of the system tends to
these equations.  Importantly, however, these stochastic equations
allow for an analysis of the swarm, as well as the ability to develop
control laws. In \cite{Li2017}, Li et al.~show that these models can
be used to develop control laws for robots in a swarm and drive them
towards a target distribution. The method is shown to perform
accurately both in simulation and on real robots. The advantage is
that guarantees can be placed on the convergence and stabilisabiilty
of the swarm towards the desired distribution. However, there appears
to be significant scope to expand upon this methodology from a safety
perspective. To begin with, the method does not consider inter-agent
interactions and therefore does not formally guard against
collisions. In \cite{Inoue2019}, a similar problem is considered,
although collisions are avoided by having the robot simply move in the
opposite direction when encountering an obstacle. It is here that the
mean-field models are not as strong since they do not take these local
interactions into account. It must be noted, however, that Inoue et
al.~(\fr{or rather the authors}) have identified this problem and are
currently working towards its incorporation into the model.

It would, therefore, be of particular interest from a safety
perspective to consider agent interactions. A starting point may be
\cite{Bellomo2017}, which extends the dynamical model of a swarm system
to include agent interaction. This presents a first step towards
considering the swarm as composed of intelligent agents rather than
mindless particles and, as the authors suggest, presents the
possibility of applying game theoretic approaches towards swarms,
which also gives the ability to consider heterogeneous swarm systems
who interact with one another through repeated play.  Similarly, it
would allow for a stronger control perspective on swarm systems such
as presented in \cite{Borzi2015}, in which a model predictive control
(MPC) scheme is presented for a leader-follower swarm system to
achieve given tasks.

@@

The reduction of the complexity in interactions between agents also
allows for the robots to perform other calculations on board. In
\cite{Pini2011TaskSelection}, Pini et al.~leverage this by considering
adaptive task partitioning across swarms. This allows a swarm, in a
decentralised manner, to deliberate whether to partition a task into
its sub-tasks or to perform the task in its whole. As of now (to the
best of my knowledge) the problem of partitioning general tasks into
its $N$ sub-tasks is unexplored. This, however, highlights another
advantage of swarm systems; they are readily divided into sub-groups
(as in \cite{Zahadat2016DivisionInhibition}) to perform a
{\em divide-et-impera}
%(divide and conquer)
approach to solving problems
\cite{Pini2011TaskSelection}).

@@

\fr{I really liked this section.}

@@

It is clear that each method presents its own set of advantages and
disadvantages. In fact, the greater contributions are made from a
unification of techniques (e.g., game theoretic control) which leverage
the strengths of one technique to mitigate the drawbacks of
another. To this end, we consider the unification of swarm control and
multi-agent learning. The aim is to unify the strengths of swarm
theory, MPC and game theory to study populations of agents who can
make decisions on an individual basis but perform tasks through large
scale collaboration. In the subsequent chapters, we propose a line of
research which explores the properties of a system as well as
establishing practical control methodologies along the way.

\fr{what about some use cases/application scenarios.}
